---
title: "Predicting the Female Pulse Rate"
format: html
editor: visual
execute: 
  echo: false
---

```{r}
#| message: false

library(tidyverse)
library(primer.data)
library(rstanarm)
```

Question of interest: What is the difference in pulse rate between two randomly selected female students in this class?

```{r}
#| message: false

glimpse(nhanes)
summary(nhanes)

x <- nhanes |> 
  select(pulse, gender) |>
  drop_na() |>
  filter(gender == "Female")

summary(x)
```

Wisdom

Units: Female students
Outcome: Pulse rates
Covariates: Gender, Age
Treatment: NA
Preceptor Table
Validity

Justice

Stability: May fail if measurement scenario is different; Data for 2010, we are measuring in 2023

Representativeness - may fail since our sample's age is younger than the age of women in the population.

Unconfoundedness - Model is not causal.

Courage to fit the model:

```{r}
x |>
  ggplot2::ggplot(aes(x = pulse)) +
  geom_histogram(bins = 40) +
  theme_minimal()

fit_obj <- stan_glm(data = x,
                formula = pulse ~ 1,
                family = gaussian,
                refresh = 0,
                seed = 9)

fit_obj
summary(fit_obj)
```

Temperance - We create posteriors of the quantities of interest. Using the model from courage to answer the questions.

```{r}
#| message: false
newobs <- tibble(.rows = 2)

pp <- posterior_predict(object = fit_obj,
                      newdata = newobs) |> 
        as_tibble()

pp

pp <- pp |>
  mutate(pulse_diff = abs(`1`-`2`))

pp |> 
  ggplot(aes(x = pulse_diff)) +
    geom_histogram(aes(y = after_stat(count/sum(count))),
                   bins = 100) +
    labs(title = "Posterior for Average Difference in Adult Female \nPulse",
         x = "Difference (Absolute Value)",
         y = "Probability",
         caption = "Data source: NHANES") + 
    scale_x_continuous(labels = scales::number_format(accuracy = 1)) +
    scale_y_continuous(labels = scales::percent_format(accuracy = 1)) +
    theme_classic() 
```