---
title: "Predicting the Female Pulse Rate"
format: html
editor: visual
execute: 
  echo: false
---

```{r}
#| message: false

library(tidyverse)
library(primer.data)
library(rstanarm)
```

Question of interest: What is the difference in pulse rate between two randomly selected female students in this class?

```{r}
#| message: false

glimpse(nhanes)
summary(nhanes)

x <- nhanes |> 
  select(pulse, gender) |>
  drop_na() |>
  filter(gender == "Female")

summary(x)
```

Wisdom

Units: Female students
Outcome: Pulse rates
Covariates: Gender, Age
Treatment: NA
Preceptor Table
Validity

Justice

Stability: May fail if measurement scenario is different; Data for 2010, we are measuring in 2023

Representativeness - may fail since our sample's age is younger than the age of women in the population.

Unconfoundedness - Model is not causal.

Formula - 

```{r}
x |>
  ggplot(aes(x = pulse)) +
  geom_histogram(bins = 40) +
  theme_minimal()

obj <- stan_glm(data = x,
                formula = pulse ~ 1
                family = guassian)
```
